The Dictionary for characters of smooth group schemes

### 2016-03-28 followup.tex
Added comparison of notation with Yu.

\begin{proof}
By continuity of $\varphi : \underline{G}(S) \to \EE^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
\underline{G}(S) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
\end{tikzcd}
\] 
Set $G_m = \Gr_m^{R}(\underline{G})$.
Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R/\mathfrak{p}^{m+1})$, canonically.
Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the linear character $\varphi_m: G_m \to \EEx$; so
\[
\trFrob{\cs{L}_m} = \varphi_m
\]
on $G_m(\Fq)$.
%
Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(\Fq)$, canonically, and comes equipped with a morphism $G \to G_m$.
Let $\cs{L}$ be the  Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \trace \varphi$.
\end{proof}

@@

Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to CC^\times$. 
The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.

The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{howe:73a}, where is it shown that $\trace(W_\psi)$ is determined by $\psi$ and its restriction to $\Sp(V)$ and, moreover, that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$. 
%
The group $\Sp(V)$ is naturally stratified into the conjugation-stable subvarieties $S_r = \{ g\in \Sp(V) \tq \dim \ker (g-1) = r \}$. 
The big stratum, $S_0$, is dense in $\Sp(V)$;
the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
From \cite{howe:73a}*{Prop. 2} we learn that $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$, for $0\leq r \leq \dim V$ and $g\in S_r$.

It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
\begin{equation}
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\end{equation}
%
Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.

Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
One begins by finding a local system $\cs{K}_0$ on $S_0 \times V^\sharp$ such that 
\[
\trFrob{\cs{K}_0[\dim V](\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
\]
where $\cs{K}_0[\dim V](\frac{\dim V}{2})$ is the Tate twist of the shift of $\cs{K}_0$.
This is done by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that 
\begin{equation}\label{Cayley}
\trace(W_\psi)(g,v,z) =  q^{-\dim V/2} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi\left(\frac{1}{4}\langle \cay(g)v,v\rangle \right) \psi(z),
\end{equation}
 for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ on $S_0 \times V^\sharp$. 
Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$. 
It follows from \cite{gurevich-hadani:07a} that 
\[
\trFrob{\cs{K}(\frac{\dim V}{2})} = \trace(W_\psi).
\]
Then $\cs{W}_\psi = \cs{K}(\frac{\dim V}{2})$ is the promised Weil sheaf complex.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%

A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
\begin{enumerate}
\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The representations $(\rho^0, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.

Since we will need some facts about this construction, we review some further detail here.

First, Yu introduces 
\begin{enumerate}
\labitem{Y3}{Y3}
compact groups $J^i\subset C$, for $i=0, \ldots d$, such that 
$
C^i = J^0\cdots J^{i}
$ 
and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J^{i+1}$ defining the groups $C^i \ltimes J^{i+1}$.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && C^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
&& C^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\end{enumerate}
%He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.

Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
$
J^{i+1} \to V_{i+1}
$
where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
%\labitem{Q2}{Q2} 
%\item 
This, in turn, is used to define a map
$
J^{i+1} \to V_{i+1}^\sharp,
$
where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism 
$
j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
$
where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
%\labitem{Q3}{Q3} 
%\item
Finally, Yu constructs 
$
f_{i+1} : C^i \to \Sp(V_{i+1}),
$
such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.

Taken together, this defines
%\end{enumerate}
\begin{enumerate}
\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
\[
\begin{tikzcd}
1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
\end{tikzcd}
\]
\end{enumerate}

We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d\otimes \varphi^d)$.
The representations $\rho^i$ are defined recursively. 
For the base case $i=0$, the representation $\rho^0$ is just $\rho_0$; see \ref{Y1} above.
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J^{i+1}$.
Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J^{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J^{i+1} \to C^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
\end{equation}
of $C^i \ltimes J^{i+1}$.
%By construction, the character of this representation satisfies
%\begin{equation}\label{eq:tilderho}
%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
%\end{equation}
%for $y \in C^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$.

This defines the representation $\rho^{i+1}$ of $C^{i+1}$. 
This completes the recursive definition and thus determines $\rho^d$. 
Now set $\rho \ceq \rho^d\otimes \varphi^d$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
%The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
%\[
%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
%\]
%for $k_i\in J^i$.

@@

%\labitem{M2}{M2}
As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
\[
\underline{J}^i \to \underline{G},
\] 
for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J^i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
%\labitem{M3}{M3}
There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
\[
\underline{G}^i \ltimes \underline{J}^{i+1}
\]
gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J^{i+1}$
%\end{enumerate}

@@

Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to V^{i+1}_\Fq$ of algebraic groups. Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
\[
\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
\]
Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
\[
\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
\]
Finally, the group homomorphism $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
\[
\underline{G}^{i}(R) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
\]

>>>>

\begin{proof}
By continuity of $\varphi : \underline{G}(S) \to \EE^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
\underline{G}(S) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
\end{tikzcd}
\] 
Set $R_m = R/\mathfrak{p}^{m+1}$ and
set $G_m = \Gr_m^{R}(\underline{G})$, the Greenberg transform of $\underline{G}\times_{\Spec{R}}\Spec{R_m}$.
Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$, canonically.
Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m \to \EEx$; so
\[
\trFrob{\cs{L}_m} = \varphi_m
\]
on $G_m(\Fq)$.
%
Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(\Fq)$, canonically, and comes equipped with a morphism $G \to G_m$.
Let $\cs{L}$ be the  Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \varphi$.
\end{proof}

@@

Let $\psi : Z \to \CC^\times$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$. 
The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.

The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{howe:73a}, where is it shown that $\trace(W_\psi)$ is determined by $\psi$ and its restriction to $\Sp(V)$ and, moreover, that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$. 
%
The group $\Sp(V)$ is naturally stratified into the conjugation-stable subvarieties $S_r = \{ g\in \Sp(V) \tq \dim \ker (g-1) = r \}$. 
The big stratum, $S_0$, is dense in $\Sp(V)$.
%the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
 From \cite{howe:73a}*{Prop. 2} we learn that if $g\in S_r$ then $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$.

It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{K}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
\begin{equation}
\trFrob{\cs{K}_\psi} = \trace(W_\psi).
\end{equation}
%
Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand since of this equality must be interpreted accordingly.

Although nothing more that this statement will be needed below, the construction of $\cs{K}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
The reader pressed for time is invited to skip the next paragraph without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.

Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
One begins by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that if $(g,v,z) \in S_0\times V\times Z$ then
\begin{equation}\label{Cayley}
\trace(W_\psi)(g,v,z) =  \frac{\gamma_\psi^{\dim V}}{q^{\dim V/2} } \sigma(\det(1+\cay(g)))\ \psi\left(\langle \cay(g)v,v\rangle/4 \right) \psi(z),
\end{equation}
 where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that 
\[
\trFrob{\cs{K}_0[\dim V](\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
\]
where $\cs{K}_0[\dim V](\frac{\dim V}{2})$ is the Tate twist of the shift of $\cs{K}_0$.
%
Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$. 
It follows from \cite{gurevich-hadani:07a} that 
\[
\trFrob{\cs{K}} = \trace(W_\psi).
\]
Then $\cs{K}_\psi$ is the promised Weil sheaf complex.

@@

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
\begin{enumerate}
\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The groups $C^i$ here are the groups $\,^\circ K^i$ in \cite{yu:01a}; the representation $\rho^0$ here is the representation $\pi_0\vert_{\,^\circ K^0}$ in \cite{yu:01a}; the quasicharacters $\varphi^i$ here are the quasicharacters $\phi_i\vert_{\,^\circ K^i}$ in \cite{yu:01a}.
%
The representation $\rho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.
%

Since we will need some facts about this construction, we review some further detail here.
In Table~\ref{table:notation} we explain how to convert the rest of the constructions appearing in this section into the notation of \cite{yu:01a}.
%
First, Yu introduces 
\begin{enumerate}
\labitem{Y3}{Y3}
compact groups $J_i\subset C$, for $i=0, \ldots d$, such that 
$
C^i = J_0\cdots J_{i}
$ 
and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J_{i+1}$ defining the groups $C^i \ltimes J_{i+1}$.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && C^{i}\cap J_{i+1}\arrow{d} && \\
1 \arrow{r} & J_{i+1} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
&& C^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\end{enumerate}
%He then introduces the following quotients of $J_{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
%
Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
$
J_{i+1} \to V_{i+1}
$
where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \EEx$.
%\labitem{Q2}{Q2} 
%\item 
This, in turn, is used to define a map
$
J_{i+1} \to V_{i+1}^\sharp,
$
where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H^{i+1}$ and an isomorphism 
$
j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
$
where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
%\labitem{Q3}{Q3} 
%\item
Finally, Yu constructs 
$
f_{i+1} : C^i \to \Sp(V_{i+1}),
$
such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.
%
Taken together, this defines
%\end{enumerate}
\begin{enumerate}
\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
\[
\begin{tikzcd}
1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
\end{tikzcd}
\]
\end{enumerate}

We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d\otimes \varphi^d)$.
The representations $\rho^i$ are defined recursively. 
For the base case $i=0$, the representation $\rho^0$ is just $\rho_0$; see \ref{Y1} above.
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J_{i+1}$.
Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J_{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J_{i+1} \to C^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
\end{equation}
of $C^i \ltimes J_{i+1}$.
%By construction, the character of this representation satisfies
%\begin{equation}\label{eq:tilderho}
%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
%\end{equation}
%for $y \in C^i \ltimes J_{i+1}$.
By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J_{i+1}$ is trivial on $C^{i}\cap J_{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$.

This defines the representation $\rho^{i+1}$ of $C^{i+1}$. 
This completes the recursive definition and thus determines $\rho^d$. 
Now set $\rho \ceq \rho^d\otimes \varphi^d$. 
This is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
%The character of $\rho^d$ on $C^d = C = J_0 \cdots J_d$ satisfies
%\[
%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
%\]
%for $k_i\in J_i$.

\begin{table}[htp]
\caption{Comparison with notation of \cite{yu:01a}}
\begin{center}
\begin{tabular}{c|l}
$C^0$ & $\,^\circ K^0 = G^i(F)_y$, \cite{yu:01a}*{\S 15} \\
$\rho^0$ & $\,^\circ \rho_0$ \cite{yu:01a}*{\S 15} \\
$C^{i+1}$ & $\,^\circ K^i = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, l\dots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
$\rho^{i+1}$ & $\,^\circ \rho_{i+1}$, \cite{yu:01a}*{\S 15} \\
$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ \\
$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
$W_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
$Z_{i+1}$ & $C$, \cite{yu:01a}*{\S 11} \\
$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} \\
\end{tabular}
\end{center}
\label{table:notation}
\end{table}%

@@

%\labitem{M2}{M2}
As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
\[
\underline{J}^i \to \underline{G},
\] 
for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
%\labitem{M3}{M3}
There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
\[
\underline{G}^i \ltimes \underline{J}^{i+1}
\]
gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J_{i+1}$
%\end{enumerate}

@@

Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J_{i+1} \to V^{i+1}$ of algebraic groups over $\Fq$. Then the quotient $J_{i+1} \to V_{i+1}$ is realized as the composition
\[
\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
\]
Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J_{i+1}\to H^{i+1}$ as the composition 
\[
\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
\]
Finally, the group homomorphism $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
\[
\underline{G}^{i}(R) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
\]
